PubCrawl: A Publication Search Engine

### 2012-05-17 report/paper.tex
Implementation section and slides from poster session.

\title{PubCrawl: A Paper Search Engine}
\author{Frank Li (frankli@mit.edu) \\
Abhishek Sarkar (aksarkar@mit.edu)\\
Manasi Vartak (mvartak@mit.edu)}
\date{May 16, 2012}

@@

@@

\section{Implementation}
\label{sec:implementation}

MANASI'S WEBSITE STUFF//
%Manasi's website stuff

For PubCrawl's implementation of the adapted PageRank scoring function, we used several parameters for variables defined in Section \ref{sec:pagerank}:\\

@@

@@

\section{Conclusion}

>>>>

\title{PubCrawl: A Publication Search Engine}
\author{Frank Li (frankli@mit.edu) \\
Abhishek Sarkar (aksarkar@mit.edu)\\
Manasi Vartak (mvartak@mit.edu)}
\date{May 16, 2012}

@@

\section{ACM Data}
%Information about ACM data

@@

\section{Implementation}
\label{sec:implementation}
\subsection{Overview}
PubCrawl is an online search website built with the Django web framework backed by a Postgres database and Lucene search index. While the Postgres database stores metadata about papers such as the citation graph, author and venue information, Lucene stores indexes for paper titles, abstracts and fulltext. The PubCrawl interface allows users to submit search terms and relative weights to be assigned to title, abstract, full text searches and pagerank. Figure \ref{interface} shows a screenshot of the interface.

\begin{figure}[t]
\centering
	\includegraphics[width=8in]{images/interface}
	\caption{PubCrawl interface allowing search term and relative weight inputs.}	
	\label{interface}
\end{figure}

\subsection{Scores and Scaling}
PubCrawl combines four scores in all - a fulltext search score, a title search score, an abstract search score and the PageRank score. Since Lucene does't score on a pre-defined scale, we normalize all Lucene. Similarly, we normalize PageRanks. We normalize all scores on a per-query basis. This is particularly relevant to PageRank since results for a particular topic may all have low PageRank since the topic is studied by few researchers. By normalizing per-query, we do not penalize topics with a small number of papers.

\subsection{Ranking}
An important challenge faced by PubCrawl is how to effectively combine the four scores above to get an over quality score for a document. We implemented two types of simple ranking functions for this purpose:

\begin{itemize}
	\item 2-factor ranking: As a first step, we only allowed full text and page rank scores to be combined. We used a simple sorting technique for this since every document returned by the search has an associated full text and page rank score.
	\item 4-factor ranking: In order to combine multiple scores, i.e., to combine multiple sorted lists, we used the RankJoin algorithm. Briefly, RankJoin is a top-k algorithm that takes multiple sorted lists and traverses them in a round-robin fashion performing hash joins on already seen tuples. It is able to stop before traversing all tuples because once the max possible score of unseen tuples becomes lesser than the minimum score of the top-k tuples, we are guaranteed to have the required top-k set of tuples. We implemented a slight variation of RankJoin since we don't need joins across all 4 lists.
\end{itemize}

\subsection{Tuning Parameters}

To tune weights for the four factors, we obtained information about seminal papers on 6 topics from experts in the respective areas. We then manually picked weights that gave good results for all 6 topics.

\subsection{PageRank Parameters}
For PubCrawl's implementation of the adapted PageRank scoring function, we used several parameters for variables defined in Section \ref{sec:pagerank}:\\

@@

To evaluate the quality of PubCrawl results, we performed a preliminary user study. In this study, we compared the quality of PubCrawl results with those from Google Scholar, Microsoft Academic Search, ACM Digital Library and CiteSeer.

\subsection{Methodology}

For 3 topics, we performed searches on Google Scholar, Microsoft Academic Search, ACM Digital Library, CiteSeer and PubCrawl. We then obtained lists of the top 10 ACM publication results from these search engines. We provided these lists to our experts. The experts rated each of the 10 results as Highly Relevant, Moderately Relevant and Not relevant. They also ranked the five lists in order of decreasing quality. Table \ref{} shows the results for the 3 test topics.

We find that PubCrawl consistently does as well as CiteSeer and ACM DL.

\subsection{Challenges}
The main challenges with evaluating the user study were (1) Ground truth wasn't always clearly known, (2) Ground-truth is subjective, (3) since the data only included ACM papers, we had to discard a large number of highly relevant but non-ACM publications.

@@

User study results.

Some time comparisons.

\section{Conclusion and Future Work}

We observed that it is very difficult to find a scoring function that works well for all search queries. We also realized that combining scores from orthogonal metrics like PageRank and text indexing may not be the best method to obtain an overall ranking.

Several extensions of this work are possible. An extremely challenging question we would like to answer is what is the best way to determine appropriate weights in a ranking function. Using labelled data points and curve fitting or SVMs, we are likely to get a better set of results. We would also like to investigate the following heuristics further: it would also be interesting to extend page rank so that it takes into account relationships between papers, i.e. paper A supports paper B, paper A refutes paper B etc. Similarly we would like to use metadata such as paper venues in order to further refine the scoring. We also looked into whether we could classify papers based on the level of expertise a paper expects. This may also be used to boost our search results.
